%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\name{Aaron K. Clark} % Your name
\address{PO BOX 97 GRAND ISLAND, NE 68959 } % Your address
\address{\href{tel:12819736082}{(281)~$\cdot$~973~$\cdot$~6082} \\ \href{mailto:cryptojones@owasp.org}{cryptojones@owasp.org}} % Your phone number and email

\begin{document}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Black Hills Information Security (Active Countermeasures)}{2024}{Senior Developer}{Remote}
	\item Windows Service Developer in .NET 8 for an Enterprise Threat-Hunting tool. Responsible for building non-native applications in a Windows Enviornment.
\end{rSubsection}

\begin{rSubsection}{CrowdStrike}{2022 - 2024}{Senior Technical Support Engineer}{Remote}
	\item SME for SaaS and on-prem LogScale(Humio), Kafka, and log shippers. Created sandbox infrastructure using terraform and k8s. Wrote automation and tooling in bash and Python.
\end{rSubsection}

\begin{rSubsection}{CloudHesive, LLC}{2021 - 2022}{Cloud Operations Supervisor}{Remote}
\item Built a team of highly technical, customer-service \& security oriented problem solvers. Supported more than 2000 customer systems on AWS, Azure, and VMWare Infrastructures. Used Datadog, SumoLogic, and NewRelic to monitor customer systems and networks. Managed backup and recovery processes. Technologies included CloudFormation, CloudWatch, EC2, EFS, ELB, IAM, RDS, S3, VPC, and Workspaces.  
\end{rSubsection}

\begin{rSubsection}{Tmutla, Inc.}{2021}{Cybersecurity Consultant}{Grand Island, Nebraska}
\item Performed Web Application Penetration tests and wrote customer reports.
\end{rSubsection}

\begin{rSubsection}{Reinke Manufacturing Company, Inc.}{2015 - 2021}{Senior Software Developer}{Remote} 
\item Led Application development of middle ware application connecting AS/400-based ERP System and WinForms Sales Application. Created the Authentication/Authorization system using ASP.NET MVC 4. Stood up and maintained Azure infrastructure for the application. Evaluated 3rd-part SAST tools and made recommendations for their implementation.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C\#, VB.NET, T-SQL, JavaScript, Powershell, Python\\
Memberships & OWASP, ACM, DC402, RITSEC, SPARSA.ORG, OperationCode\\
Certifications & SSCP, AWS CCP, AWS SAA, A+, Network+, CCNA (expired), MCSA
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

I have been awarded a \href{https://raw.githubusercontent.com/CryptoJones/cv/master/RIT_MMM.pdf}{MicroMaster's in Cybersecurity} from RIT, Graduate Certificates in  \href{https://raw.githubusercontent.com/CryptoJones/cv/master/CSU_GRADCERT_ITPM.jpg}{IT Project Management} from Colorado State University and \href{https://raw.githubusercontent.com/CryptoJones/cv/master/KSU_GRADCERT_CSF.jpg}{Computer Science} from Kennesaw State University. 

I also have a \href{https://github.com/CryptoJones/cv/raw/master/UMUC_UNDERGRAD_DIPLOMA.jpg}{Bachelor of Science} from the University of Maryland University College in Computer and Information Science. 

For my full academic CV, see: \href{https://github.com/CryptoJones/cv/raw/master/Clark\%2C\%20Aaron\%20K.\%20-\%20CV.pdf}{https://github.com/cryptojones/cv}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
